%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week:}

\emph{project 1: Making games for assembly}
\begin{itemize}
\item Getting data and analyze data from the four games.
\item Make the first draft of the paper
\item Make the new games with the feedback we got.
\end{itemize}




\section{My \emph{Accomplishments} this week}


\begin{itemize}
\item made the plots for varying visualization. Computed p values, none of them were interesting. Seemed all the players did full-state. Even removing outliers didn't help.
\item We made the four new games. varying noise, shape size, number of robots, and density.
\item Now the robots are distributed uniformly, the orientation has changed and the games are harder and the solution is less memorizable. 
\item The smart phone also works, so we can get more data.
\item size of the robots are the same when we change number of robots.
\item Smaller bugs have been resolved(the color of the dots, not overlapping robots, the overviews of the games, goals, etc)
\end{itemize}


\section{My \emph{Plan} for next week}

\begin{itemize}
\item Get data from the users and see if the new results have something interesting.
\item Complete the paper for Multirobot conference.
\item Have at least one experiment with the real robots and assemble them(One full run for Shiva and one full run for Lillian)
\item Do the torque experiments with the new design and see if the new design works better.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item Discuss the results and choose some interesting result from them
\end{itemize}

\end{document}
