%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week:}

\emph{project 1: Making games for assembly}
\begin{itemize}
\item Making 4 new games for assembly varying visualization
\end{itemize}

\emph{project 2: Torque Control Journal}
\begin{itemize}
\item Experiments with the different goal positions to make torque
\item Make the new object to keep the robots go straight
\end{itemize}

\emph{project 3: using friction for finding the shortest path}
\begin{itemize}
\item solve the equations for finding the shortest path in circle
\end{itemize}




\section{My \emph{Accomplishments} this week}


\begin{itemize}
\item All shapes are made and the games are doable, but the goal is still not correct.
\item We made the object for torque control experiment.
\item Tried to solve the equations, (I gave them to you) but it is still unsolved.
\end{itemize}


\section{My \emph{Plan} for next week}

\begin{itemize}
\item Complete the games (make the goals correct) and get data from people (at least people in the lab).
\item Continue trying to solve the equations for the shortest path in circle
\item make the draft of the paper.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item play my games!
\item start the draft and get ideas on the paper which is due on June 10th.
\item Get ideas on how to calculate the equations!
\end{itemize}

\end{document}
