%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week}
\begin{itemize}
\item Having 5 full experiments of block pushing
\end{itemize}



\section{My \emph{Accomplishments} this week}


\begin{itemize}
\item We were able to make one full experiment
\item Mable made the simulation of getting out of stuck and I debugged it.
\item Lillian and I wrote the thresholding part (which I discussed with you) and debugged it.
\item I debugged the previous code and tuned the variances, the corners, the delay time, and all the possible variables to tune
\item I found out how to simultaneously record the raw video and matlab video. (I will get the raw video with quick time, in our code we have lots of pause commands which are bad for the raw video if we wanted to save the raw video with matlab)
\item We made the object lighter.
\item Today we had outreach!
\end{itemize}


\section{My \emph{Plan} for next week}

\begin{itemize}
\item I want to implement the partitioning part with map. I have to write an algorithm for that and load that.
\item I hope to be able to finish at least 4 more full experiments and also write all the missing part of the paper.
\item I would start the torque control journal paper with Mable and Lillian, I want to start with the pure torque control task this week and write the code for that.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item My main discussion would be on the algorithm if I was not able to figure it out myself.
\end{itemize}

\end{document}
