%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week}
\begin{itemize}
\item Working on the project for Dr. Kavraki's Class
\item Starting the torque journal paper
\end{itemize}



\section{My \emph{Accomplishments} this week}


\begin{itemize}
\item I started project 3 for Dr. Kavraki's class. In this project we use ompl to implement a simple planner. I am grouped with Mary, and responsible for Exercise 1 and 2 which is implementing the planner. Mary is responsible to test the planner and compare it with other planners, as well as writing the report for the project.
\item Writing the equations for challenge 1 in latex. I am still working on it.
\item I changed some of the pictures of the case paper for the journal version
\item I downloaded the template for Science Robotics, I started working on that template, but I think that this paper might not fit to that journal. We can discuss about it.


\section{My \emph{Plan} for next week}

\begin{itemize}
\item I would finish writing the math for pure torque control.
\item I want to read Kevin Lynch's paper
\item I would add plots of the the first two challenges to the paper.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item Discuss about the math for the two challenges.
\item Discuss about the scope of the paper and if it fits Science Robotics
\item Should we have a meeting with the professor in nano lab?
\end{itemize}

\end{document}
