%%%% Weekly Report Information %%%%
\newcommand{\handoutName}{Weekly report}
\newcommand{\handoutdate}{\today}
%\newcommand{\duedate}{}
\input{Header.tex}

\section{My \emph{Objectives} this week}
\begin{itemize}
\item Complete Uniform distribution torque analysis for pivoted object,
\item Complete Uniform distribution torque analysis for free object,
\item Complete triangular distribution torque analysis for pivoted object,
\item Complete triangular distribution torque analysis for free object,
\item Try normal distribution for free object and see if analytically we can solve it.
\end{itemize}



\section{My \emph{Accomplishments} this week}


\begin{itemize}
\item Completed the uniform distribution analysis. for both pivoted and free.
\item completed the triangular distribution analysis for pivoted object.
\item have some problems understanding the techniques used for normal distribution finding limit.
\end{itemize}


\section{My \emph{Plan} for next week}

\begin{itemize}
\item Complete triangular distribution for free object
\item Understand why Dr. B's analysis for normal distribution is correct, and try to do the same thing for free object.
\item Write up all the stuff in the new organized mathematica code, and correct sections and subsections in the draft.
\item Think about angle of repos. And also making the problem statement for using probabilistic motion planning for the object in the configuration space with some obstacles.
\end{itemize}

\subsection{Meeting with Dr. Becker  }

\begin{itemize}
\item Discuss about the results and make sure if all of them make sense and are correct.
\item Discuss about the problem statement of the motion planning with obstacles.
\item Editing the draft and see if they are suitable for a short journal publication.
\end{itemize}

\end{document}
